Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-03-29 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: make tables uniform and cosmetics to the contour plot

\begin{table}[h]
\begin{tabular}{l l c c c}
\hline
\hline
$N_{\rm max}$ & Event & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
              &       & bound? & bound?  &                            \\
\hline
  & GW150914  & Yes & Yes &  $38.2$~km \\
0 & GW200129  & Yes & Yes &  $42.5$~km \\
  & Combined  &     &     &  \cellcolor{black!10}$38.2$~km \\
\hline
  & GW150914  & Yes  & No  &  -- \\
1 & GW200129  & Yes  & No  &  -- \\
  & Combined  &      &     &  -- \\
\hline
\hline
\end{tabular}
\caption{Detailed summary of our results the cubic EFT of GR for GW150914, GW200129, and
combined events using $\gm = M_{f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
}
\label{tab:summary_ceft}
\end{table}

@@

\begin{table}[h]
\begin{tabular}{l l c c c}
\hline
\hline
$N_{\rm max}$ & Event & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
              &       & bound? & bound?  &                            \\
\hline
  & GW150914 & Yes & Yes  & $51.7$~km \\
0 & GW200129 & Yes & Yes  & $54.8$~km \\
  & Combined &     &      & \cellcolor{black!10}$51.3$~km \\
\hline
  & GW150914 &  &     &    \\
1 & GW200129 &  &     &    \\
  & Combined &  &     &    \\
\hline
\hline
\end{tabular}
\caption{Detailed summary of our results the quartic EFT of GR for GW150914, GW200129, and
combined events using $\gm = M_{f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
%
}
\label{tab:summary_qeft}
\end{table}

>>>>

\begin{table}[h]
\begin{tabular}{l l c c c}
\hline
\hline
$N_{\rm max}$ & Event & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
              &       & bound? & bound?  &                            \\
\hline
  & GW150914  & Yes & Yes &  $\ell_{\rm cEFT} \leqslant 38.2$~km \\
0 & GW200129  & Yes & Yes &  $\ell_{\rm cEFT} \leqslant 42.5$~km \\
  & Combined  &     &     &  \cellcolor{black!10}$\ell_{\rm cEFT} \leqslant 38.2$~km \\
\hline
  & GW150914  & Yes  & No  &  -- \\
1 & GW200129  & Yes  & No  &  -- \\
  & Combined  &      &     &  -- \\
\hline
\hline
\end{tabular}
\caption{Detailed summary of our results the cubic EFT of GR for GW150914, GW200129, and
combined events using $\gm = M_{f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
}
\label{tab:summary_ceft}
\end{table}

@@

\begin{table}[h]
\begin{tabular}{l l c c c}
\hline
\hline
$N_{\rm max}$ & Event & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
              &       & bound? & bound?  &                            \\
\hline
  & GW150914 & Yes & Yes  & $\ell_{\rm qEFT} \leqslant 51.7$~km \\
0 & GW200129 & Yes & Yes  & $\ell_{\rm qEFT} \leqslant 54.8$~km \\
  & Combined &     &      & \cellcolor{black!10}$\ell_{\rm qEFT} \leqslant 51.3$~km \\
\hline
  & GW150914 &  &     &    \\
1 & GW200129 &  &     &    \\
  & Combined &  &     &    \\
\hline
\hline
\end{tabular}
\caption{Detailed summary of our results the quartic EFT of GR for GW150914, GW200129, and
combined events using $\gm = M_{f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
%
\hs{Need to debug $N_{\rm max} = 1$ runs.}
%
}
\label{tab:summary_qeft}
\end{table}
